Parity games in pushdown systems with pebbles

### 2023-06-12 reachability/article.tex
up

Hence we propose in this paper to extend pushdown systems with a set of 
parameters.
%
% Compared to pebble word automata, instead of using pebbles
% as markings on their input, pebble pushdown systems have the ability to lift or drop pebbles
% on their universe of stack contents. Dropping a pebble records the current stack content with an available pebble until it is lifted. Lifting a pebble then makes it available again.

@@

Another closely related formalism is that of alternating tree automata with nested pebbles, as we 
consider in more details in Section 4. The approach of extending tree automata with pebbles was used in \cite{milo2000typechecking} to show that the XML typechecking problem is decidable, and in \cite{karhumaki2012jewels} to recognize first-order logic on trees. In both cases however, the input trees considered are finite, while 
simulation of plays in parametric pushdown graphs
requires the use of pebble alternating tree automata working on infinite trees
since the stack of a pushdown system is in general unbounded.

@@

In Section 2, we provide general notations and preliminary definitions. Section 3 will deal with the introduction of pebble pushdown games.
Section 4 is devoted to using pebble alternating tree automata with parity acceptance condition to solve pebble pushdown system parity games. We leave the proof of decidability itself  for Section 5.
Section 6 at last shows a nonelementary lower bound for the problem.

>>>>

% Hence we propose in this paper to extend pushdown systems with a set of  parameters.
%
% Compared to pebble word automata, instead of using pebbles
% as markings on their input, pebble pushdown systems have the ability to lift or drop pebbles
% on their universe of stack contents. Dropping a pebble records the current stack content with an available pebble until it is lifted. Lifting a pebble then makes it available again.

@@

Another closely related formalism is that of alternating tree automata with nested pebbles%, as we consider in more details in Section 4
. The approach of extending tree automata with pebbles was used in \cite{milo2000typechecking} to show that the XML typechecking problem is decidable, and in \cite{karhumaki2012jewels} to recognize first-order logic on trees. In both cases however, the input trees considered are finite, while 
simulation of plays in parametric pushdown graphs
requires the use of pebble alternating tree automata working on infinite trees
since the stack of a pushdown system is in general unbounded.

@@

In Section 2, we provide general notations and preliminary definitions. Section 3 will deal with the introduction of 
parametric pushdown games.
% Section 4 is devoted to using pebble alternating tree automata with parity acceptance condition to solve parametric pushdown system parity games. We leave the proof of decidability itself  for Section 5.
Section 6 at last shows a nonelementary lower bound for the problem.
